%===============================================================================
% Valentin
%===============================================================================

\subsection{CV for Valentin V\"olkl}
\begin{description}
\item[] CERN
\item[] Espl. des Particules 1 - Geneva (Switzerland)
\item[] valentin.volkl@cern.ch
\end{description}

\subsection*{Education}
\begin{description}
    \item[] PhD in Particle Physics: 2021, Innsbruck University (Austria)
    \item[] Masters in Physics, 2015, Innsbruck University (Austria)
\end{description}

\subsection*{Professional Experience}
\begin{description}
    \item[] 2023--present: Systems Software Engineer, CERN (Switzerland)
\end{description}

\subsection*{Tools}

\begin{itemize}
    \item[] CVMFS: a scalable, reliable and low-maintenance software distribution service
    \\Lead developer \& release manager (2023--present)
    \\{\small{\url{https://cernvm.cern.ch/fs} - \url{https://cvmfs.readthedocs.io}}}
    \item[] Key4hep: A full software stack for future collider experiments\\Developer (2020-2023)\\{\small{ \url{https://github.com/key4hep/}}}
\end{itemize}

\subsection*{Conferences, Workshops and Tutorials}

\begin{itemize}
\item[] Organisation of \emph{CernVM} workshop in
        \href{https://indico.cern.ch/e/cvm24}{Geneva (2024)}.


\item[] {\emph{ Key4hep: Progress on Common Software }, Talk at { LCWS 2021}}
\item[] {\emph{ CERN R\&D on Spack and the Turnkey Stack}, Talk at {HSF WLCG Virtual Workshop}}
\item[] {\emph{ First performance results for Liquid Argon Calorimetry for FCC-ee}, Talk at { FCC Week 2019, Brussels}}
\item[] {\emph{ Combined reconstruction with tracker and calorimeter}, Talk at { FCC Week 2019, Brussels}}
\item[] {\emph{ Timed Track Seeding to mitigate pile-up effects}, Talk at FCC week
2018, Amsterdam} 
\end{itemize}

\subsection*{Selected Publications}


\begin{itemize}

\item[] L. Promberger, V. V\"olkl, M. Harvey, J. Blomer, \emph{CernVM-FS at Extreme Scales}. EPJ Web Conf. 295 (2024) 04012. Contribution to: CHEP 2023, Norfolk VA, USA.

\item[] {M. Mangano and others (FCC Collaboration). \emph{Future Circular Collider Conceptual
Design Report, Vol. 1 : Physics opportunities. } Technical Report CERN-ACC-2018-0056, CERN, Geneva,
Dec 2018.  \url{http://cds.cern.ch/record/2651294}.  Eur. Phys. J. C.} \\

\item[] {M.  Benedikt  and  others  (FCC  Collaboration). \emph{Future  Circular  Collider
Conceptual  Design  Report,  Vol.  2:  The  Lepton  Collider  (FCC-ee).}   Technical Report
CERN-ACC-2018-0057, CERN, Geneva, Dec  2018.   \url{http://cds.cern.ch/record/2651299}. Eur. Phys. J. ST.} \\


\end{itemize}

